P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2024-06-29 manuscript.tex
More updates
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

Where $k^{n}$ is the spring stiffness, $\xi^{n}$ the normal velocity damping, $\mu$ the friction, and $\delta_{ij}$ the penetration depth.
The update rule \autoref{eq:update_rule} and modifications in \autoref{eq:linear_spring_dashpot_tangential} were properly included to fix frictional contact accordingly \cite{dem1,dem2}.
The update rule is carried out every time-step the contact persists, which from the algorithmic point of view means that a contact history data structure is needed to properly compute these interactions.

>>>>

Where $k^{n}$ is the spring stiffness, $\xi^{n}$ the normal velocity damping, $\mu$ the friction, and $\delta_{ij}$ the penetration depth.
The update rule \autoref{eq:update_rule} and modifications in \autoref{eq:linear_spring_dashpot_tangential} were properly included to fix frictional contact accordingly \cite{dem1,dem2}.
The tangential spring displacement $\hat{\delta}^{t}_{ij}$ is initialized as a zero vector in the first contact between the particles $i$ and $j$, and the update rule is carried out every time-step the contact persists.
From the algorithmic point of view, this means that a contact history data structure is required to keep track of the last updated value.
